\documentclass{academiccv}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{hyperref}

\begin{document}
\raggedright

% display name as the document title
\namefont{\myname}\\
\vspace{1em}
\textcolor{darkgray}{{\Large Data Analyst}}

% contact info
\vspace{1em}
\begin{minipage}[t]{0.495\textwidth}
  \href{mailto:natera@hey.com}{natera@hey.com}\\
  \href{https://luisnatera.com}{luisnatera.com} \\
  +36-30-846-91-65
\end{minipage}
\begin{minipage}[t]{0.495\textwidth}
	\href{https://github.com/nateraluis}{GitHub.com/NateraLuis}\\
	\href{https://www.linkedin.com/in/natera/}{Linkedin.com/in/Natera} \\
	
  \end{minipage}
\vspace{2.5em}

Motivated, interdisciplinarity team-work oriented, and responsible Data Analyst with significant experience working in urban mobility and data analysis. Highly educated, finishing a Ph.D. in Network Science from the Central European University, where I developed new data methods for the analysis of large-scale urban mobility network data, along with the designing of new algorithms to quantify urban liveability and connectivity improvement for bicycle infrastructure networks.\\
I am interested in the intersection between data analysis and urban mobility as a way to improve our cities towards a more sustainable future.

\section*{Education}
\begin{tablist}
	\item[Ph.D.] \tab Network Science, Central European University, Budapest, Hungary. 2021 (expected) 
	\item[M.A.]  \tab Communication of Science and Culture, ITESO, Tlaquepaque, Mexico. 2015 \\
		\subitem\textbf{Academic Visit.} Center for Civic Media, MIT Media Lab, Boston, USA. 2015
	\item[B.Arch.]  \tab Architecture,  ITESO, Tlaquepaque, Mexico. 2010
		\subitem\textbf{Academic Visit.} Universidad de Valparaíso, Valparíso, Chile. 2012 
\end{tablist}

\section*{Technical Skills}
\begin{list}{}{}
	\item[\textbf{Data Management}] \tab PostgreSQL, PostGIS, Data Analysis, Pattern \& Trend Identification, Data Visualization 
	\item[\textbf{Computational tools}] \tab Python (+5 years experience), Jupyter Notebooks \& Jupyter Lab stack, Django (intermediate), HTML (intermediate), CSS (intermediate), Javascript (beginner), SQL (intermediate), \LaTeX (intermediate), Git + {GitHub, GitLab, Bitbucket}, Ci/Cd
	\item[\textbf{Research methods}] \tab Network \& data science research methodologies, Data mining, Statistical analysis
\end{list}

\section*{Work Experience}
\subsection*{Agglomeration and Social Networks research Lab}
\textcolor{darkgray}{{\large Research fellow}}\\
\textcolor{gray}{{\small 07/2021 - Present}}\\
\begin{list}{}{}
  \item{\textbf{Urban mobility and COVID-19}}
  \subitem{Analyzed mobility data (GPS traces) to model and provide insights regarding the impact of COVID-19 in the urban mobility of Budapest. The analysis has the objective to understand where are the most susceptibles areas in a city to be economically afected by the lack human movement.}
  \subitem{\textbf{Technology stack:} Python (OSMnx, igraph, GeoPandas, movingPandas, and more.), PostgreSQL, PostGIS, Linux Server, Google Maps API, and more.} 
\end{list}
\vspace{0.5em}

\subsection*{Cities Observatory (ITESM)}
\textcolor{darkgray}{{\large Data and network science consultant}}\\
\textcolor{gray}{{\small 05/2020 - Present}}\\
\begin{list}{}{}
  \item{\textbf{Accesibility and mobility analysis}}
  \subitem{Help and coordinate with the data science team the developing of a methodology to measure urban accesibility in 75 mexican cities using open data, such as OpenStreetMap, national directory of economic units, and other sources.}
  \subitem{\textbf{Technology stack:} Python (OSMnx, igraph, GeoPandas, Matplotlib, and more.), PostgreSQL, PostGIS, AWS (RDS, S3, EC2) and more.} 
  \item{\textbf{Air quality during COVID-19 pandemic lockdown}}
  \subitem{Design and develop a method to measure the changes in air quality for the cities of Mexico City, Guadalajara, and Monterrey during the lockdown of the COVID-19 pandemic, and the impact of reduce urban mobility.}
  \subitem{\textbf{Technology stack:} Python (OSMnx, GeoPandas, Pandas, and more).} 
\end{list}
\vspace{0.5em}

\subsection*{LAC\_analytics}
\textcolor{darkgray}{{\large Co-founder}}\\
\textcolor{gray}{{\small 01/2020 - Present}}\\
\begin{list}{}{}
  \item{\textbf{City Intelligence}}
  \subitem{Development of a data-driven web platform and API for the analysis of cities and amenities. Some applications of the platform and the data are: location intelligence for real estate, traffic, and public transport, and the analysis of the urban mobility of the city.}
  \subitem{\textbf{Technology stack:} Django, Python for data processing, PostgreSQL, PostGIS, AWS (RDS, S3, EC2), HTML, JavaScript.} 
  \item{\textbf{Evaluation of air quality and urban environment}}
  \subitem{Development and coordination for a methodology to estimate the quality of air in the area where a new public transport system is being built. The collected data was used to create a baseline to compare the quality of air in the area befor and after the new transport system starts opperating. This project was a collaboration within multiple actors, including Google.org, and the Government of Jalisco.}
  \subitem{\textbf{Technology stack:} Python (GeoPandas, Pandas, Matplotlib, and more), APIs.} 
\end{list}
\vspace{0.5em}

\subsection*{Central European University}
\textcolor{darkgray}{{\large Ph.D. Researcher}}\\
\textcolor{gray}{{\small 08/2017 - Present}}\\
\begin{list}{}{}
  \item{\textbf{Multimodal Fingerprint of Urban Transportation Networks}}
  \subitem{Development of a methodology and computational methods for the analysis of urban form in multiple cities around the world. The detection of patterns in the urban mobility infrastructure is useful to understand the urban mobility of a city, and to predict the future of the city.}
  \subitem{\textbf{Technology stack:} Python (data collection, cleaning, and modeling), Linux Servers.} 
  \item{\textbf{Bicycle infrastructure network analysis}}
  \subitem{Development of algorithms to evaluate and improve the connectivity of bicycle infrastructure networks. The algorithms where applied to fifteen different cities in the world, and the results were published in the journal Royal Society Open Science.}
  \subitem{\textbf{Technology stack:} Scientific Python (data collection, cleaning, and modeling), QGIS, Linux Servers.} 
  \item{\textbf{Quantifying life quality as walkability}}
  \subitem{Analysis of pedestrian urban accesibility metrics to quantify the liveability of a given city. The project was developed for the Budapest municiaplity as part of a strategy to dectect oportunities around the city and to develop data-driven public policies.}
  \subitem{\textbf{Technology stack:} Scientific Python (data collection, cleaning, and modeling), Linux Servers, Statistical modelling.} 
\end{list}
\vspace{0.5em}

\subsection*{Signa\_Lab}
\textcolor{darkgray}{{\large Executive Coordinator}}\\
\textcolor{gray}{{\small 08/2016 - 08/2017}}\\
\begin{list}{}{}
  \item{\textbf{Online social networks analysis}}
  \subitem{Executive coordinator of a social media analysis laboratory. I coordinated the research and development of methodologies to analyze social media data (Twitter, Facebook, and Youtube) to identify patterns and trends in online conversation.}
  \subitem{\textbf{Technology stack:} Python (data collection, cleaning), Gephi, Tableau.}  
\end{list}
\vspace{0.5em}

\subsection*{Mesura}
\textcolor{darkgray}{{\large Networks Analyst}}\\
\textcolor{gray}{{\small 10/2015 - 08/2017}}\\
\begin{list}{}{}
  \item{\textbf{Online social networks analysis}}
  \subitem{Analyst of social networks, I worked with multinational clients to analyze and improve their social media presence. I developed tools to automatize the data collection with the use of APIs.}
  \subitem{\textbf{Technology stack:} Python (data collection), Gephi, Tableau.}  
\end{list}
\vspace{0.5em}

\subsection*{IMTJ (Mobility Institute of the State of Jalisco)}
\textcolor{darkgray}{{\large Analyst}}\\
\textcolor{gray}{{\small 1/2015 - 10/2015}}\\
\begin{list}{}{}
  \item{\textbf{Sustainable urban mobility}}
  \subitem{Analyst of urban mobility, I worked with a team of urban and mobility planners to develop the public policies and technical specifications for the operation of the first bike share system in Gudalajara, Jalisco. México. The project was a collaboration with the Government of Jalisco and the municipalities of Guadalajara and Zapopan.}
  \subitem{\textbf{Technology stack:} AutoCAD, QGIS.}  
\end{list}
\vspace{0.5em}

\subsection*{Colectivo Triciclo}
\textcolor{darkgray}{{\large Co-Founder, Principal Architect}}\\
\textcolor{gray}{{\small 8/2010 - 1/2015}}\\
\begin{list}{}{}
  \item{\textbf{Architecture and urban design}}
  \subitem{I cofounded my own architecture studio. I was responsible for the design of private houses and the development of urban interventions, such as a pop-up neighborhood reading quiosc.}
  \subitem{\textbf{Technology stack:} AutoCAD, QGIS.}  
\end{list}
\vspace{0.5em}

\section*{Other Work Experience}
\subsection*{Teaching}
\textcolor{gray}{{\small 07/2017 - Present}}\\
\begin{list}{}{}
  \item{\textbf{Python for Social Scientist}}
  \subitem{I have taught introductory Python courses for social scientists in multiple places, such as Leibniz Institute for the Social Sciences, European Consortium of Political Research, and the Central European University.}
  \subitem{\textbf{Technology stack:} Jupyter Notebooks, Google Colab.} 
  \item{\textbf{Introduction to Network Science}}
  \subitem{I have taught deveolped and taught introduction courses to Network Science for non-technical people in interdiscipliary settings. Such courses were developed to facilitate the undestangind of complex systems in a friendly and interactive way.}
  \subitem{\textbf{Technology stack:} Jupyter Notebooks, Google Colab, offline activities.} 
\end{list}
\vspace{0.5em}


\section*{Awards}
\begin{tablist}
	\item[2020] \tab Award for Advanced Doctoral Students. Central European University 
	\item[2019] \tab Best lighting talk award. International Conference in Complex Networks and their Applications. 
\end{tablist}


\section*{Professional Affiliations and Service}
\subsection*{Professional Affiliations}
\begin{itemize}
	\item Network Science Society
	\item Python Software Foundation
	\item SICC Italian Society for Chaos and Complexity
\end{itemize}
\subsection*{Service}
\begin{itemize}
	\item Scientific Data Reviewer
	\item Ph.D. program representative, Central European University, DNDS, 2019-20
	\item Co-organizer Data Stories visualization exhibition, Central European University, DNDS, 2018-19
\end{itemize}


\section*{Languages}
\begin{itemize}
	\item Spanish \tab Native
	\item English \tab Professional proficiency
\end{itemize}

% display today's date as Month Year after a vertical space below the end of the text
\begin{center}
\vspace{6em}
%\vfill
Updated \monthyeardate\today
\end{center}

\newpage

\section*{Appendix}

\section*{Academic Publications}
\begin{tablist}
	\item[2020] \tab Natera Orozco, L. G., Battiston, F., I\~niguez, G., Szell, M. \enquote{Data-driven strategies for optimal bicycle network growth} \textit{Royal Society Open Science}, 2020. \textbf{7}: 201130. \url{https://doi.org/10.1098/rsos.201130}

	\item[2020] \tab Natera Orozco, L.G., Battiston, F., I\~niguez, G., Szell, M. \enquote{Extracting the multimodal fingerprint of urban transportation networks} \textit{Transport Findings}, 2020. \url{https://doi.org/10.32866/001c.13171}
	\item[2019] \tab Natera Orozco, L. G., Deritei, D., Vancso, A., Vasarhelyi, O. \enquote{Quantifying life quality as walkability on urban networks} In: Cherifi H., Gaito S., Mendes J., Moro E., Rocha L. (eds) \textit{Complex Networks and Their Applications VIII. COMPLEX NETWORKS 2019. Studies in Computational Intelligence}, 2019, pp. 905–918. 
	\item[2019] \tab Natera Orozco, L. G. \enquote{Un cambio de la comunicación gubernamental y política. De los medios de comunicación a las redes sociales.} \textit{Informe Anual Q Medios 2018}, edited by Bernal, G. Jalisco, Mexico: ITESO.
	\item[2018] \tab Natera Orozco, L. G., Reguillo, R. \enquote{Comunicación y cambio social: participación política e internet en Jalisco} \textit{Enciclopedia Jaliscience de la Comunicación.}, edited by Orozco, G., Reguillo, R. Jalisco, Mexico: Universidad de Guadalajara. 
	\item[2016] \tab Natera Orozco, L. G., (as Signa\_Lab) \enquote{Battle of the hashtags: Mapping the online conversation surrounding Mexico's gas price} \textit{Global Voices.} 
	\item[2014] \tab Natera Orozco, L. G. \enquote{Comunicación, ciudad e internet: flujos de información urbana en entornos digitales} VI Seminatio Internacional de Investigación en Urbanismo. Bogota, Colombia. 
\end{tablist}

\subsection*{Manuscripts in Preparation and Development}
\begin{tablist}
	\item[\the\year] \tab Natera Orozco, L. G., Alessandretti, L., Szell, M., Battiston, F. \enquote{Multimodal transportation and mobility in urban networks} Under review at \textit{Transportation}
	\item[\the\year] \tab Tupikina, L., Natera Orozco, L. G., Battiston, F. \enquote{A comparative analysis of station and dockless bike share systems.} 
\end{tablist}

\section*{Conference and Invited Talks}
\begin{tablist}
	\item[2021] \tab \textit{Invited talk:} Bauhaus-Universität Weimar, Germany. 
	\item[2021] \tab \textit{Invited talk:} URBANUM. Budapest, Hungary.
	\item[2021] \tab \textit{Invited talk:} Graph data science. Manning Publications.
	\item[2020] \tab \textit{Invited talk:} Science, Technology and Innovation Council. Hidalgo, Mexico.
	\item[2020] \tab \textit{Invited talk:} Neo Urban Networks Workshop. Paris, France.
	\item[2020] \tab \textit{Invited talk:} PIP Ciudad Futuro. Guadalajara, Mexico.
	\item[2019] \tab \textit{Conference:} VIII Conference in Complex Networks and their Applications. Lisbon, Portugal.
	\item[2019] \tab \textit{Invited talk:} Data Science MeetUp. Timisoara, Romania.
	\item[2019] \tab \textit{Invited talk:} FabLab, West University of Timisoara. Timisoara, Romania.
	\item[2019] \tab \textit{Conference:} Cycling Research Board Meeting. Delft, Netherlands.
	\item[2019] \tab \textit{Invited talk:} 4D Cities, Multi-Actor Systems Department, TU Delft. Delft, Netherlands.
	\item[2019] \tab \textit{Invited talk:} Mobile and Social Computing Lab, Fondazione Bruno Kessler. Trento, Italy.
	\item[2019] \tab \textit{Conference:} The Network Science Society Conference. Burlington, USA.
	\item[2019] \tab \textit{Invited talk:} ANET-Talks, ANET Lab, Hungarian Academy of Science. Budapest, Hungary.
	\item[2018] \tab \textit{Invited talk:} Signa\_Lab, ITESO. Tlaquepaque, Mexico.
	\item[2018] \tab \textit{Conference:} SICC Workshop ComplexCity@PoliTo. Turin, Italy. 
	\item[2015] \tab \textit{Invited talk:} Encuentro de Urbanismo Alternativo, Centro Cultural de España en México. Mexico City, Mexico.
	\item[2015] \tab \textit{Invited talk:} II Simposio de ciudades y territorios incluyentes \enquote{Derecho a la Ciudad}, Universidad Autónoma de Yucatán. Merida, Mexico.
	\item[2013] \tab \textit{Conference:} Future of Places. Stockholm, Sweden.
\end{tablist}


% \section*{Publications}
% \subsection*{Peer-Reviewed Journal Articles}
% \begin{tablist}
% 	\item[2020] \tab Natera Orozco, L. G., Battiston, F., I\~niguez, G., Szell, M. \enquote{Data-driven strategies for optimal bicycle network growth} \textit{Royal Society Open Science}, 2020. \textbf{7}: 201130. \url{https://doi.org/10.1098/rsos.201130}

% 	\item[2020] \tab Natera Orozco, L.G., Battiston, F., I\~niguez, G., Szell, M. \enquote{Extracting the multimodal fingerprint of urban transportation networks} \textit{Transport Findings}, 2020. \url{https://doi.org/10.32866/001c.13171}
% \end{tablist}

% \subsection*{Journal Article Manuscripts under Peer Review}
% \begin{tablist}
% 	\item[\the\year] \tab Natera Orozco, L. G., Alessandretti, L., Szell, M., Battiston, F. \enquote{Multimodal transportation and mobility in urban networks} Under review at \textit{Transportation}
% \end{tablist}

% \subsection*{Peer-Reviewed Conference Proceedings}
% \begin{tablist}
% 	\item[2019] \tab Natera Orozco, L. G., Deritei, D., Vancso, A., Vasarhelyi, O. \enquote{Quantifying life quality as walkability on urban networks} In: Cherifi H., Gaito S., Mendes J., Moro E., Rocha L. (eds) \textit{Complex Networks and Their Applications VIII. COMPLEX NETWORKS 2019. Studies in Computational Intelligence}, 2019, pp. 905–918.
% 	\item[2014] \tab Natera Orozco, L. G. \enquote{Comunicación, ciudad e internet: flujos de información urbana en entornos digitales} VI Seminatio Internacional de Investigación en Urbanismo. Bogota, Colombia.
% \end{tablist}

% \subsection*{Peer-Reviewed Book Chapters}
% \begin{tablist}
% 	\item[2019] \tab Natera Orozco, L. G. \enquote{Un cambio de la comunicación gubernamental y política. De los medios de comunicación a las redes sociales.} \textit{Informe Anual Q Medios 2018}, edited by Bernal, G. Jalisco, Mexico: ITESO.
% 	\item[2018] \tab Natera Orozco, L. G., Reguillo, R. \enquote{Comunicación y cambio social: participación política e internet en Jalisco} \textit{Enciclopedia Jaliscience de la Comunicación.}, edited by Orozco, G., Reguillo, R. Jalisco, Mexico: Universidad de Guadalajara.
% \end{tablist}

% \subsection*{Reviews and Other Articles}
% \begin{tablist}
% 	\item[2016] \tab Natera Orozco, L. G., (as Signa\_Lab) \enquote{Battle of the hashtags: Mapping the online conversation surrounding Mexico's gas price} \textit{Global Voices.}
% \end{tablist}

% \subsection*{Manuscripts in Preparation and Development}
% \begin{tablist}
% 	\item[\the\year] \tab Tupikina, L., Natera Orozco, L. G., Battiston, F. \enquote{A comparative analysis of station and dockless bike share systems.} 
% \end{tablist}


% \section*{Invited Talks}
% \begin{tablist}
% 	\item[2021] \tab Bauhaus-Universität Weimar, Germany.
% 	\item[2021] \tab URBANUM. Budapest, Hungary.
% 	\item[2021] \tab Graph data science. Manning Publications. Online.
% 	\item[2020] \tab Science, Technology and Innovation Council. Hidalgo, Mexico.
% 	\item[2020] \tab Neo Urban Networks Workshop. Paris, France.
% 	\item[2020] \tab PIP Ciudad Futuro. Guadalajara, Mexico.
% 	\item[2019] \tab Data Science MeetUp. Timisoara, Romania.
% 	\item[2019] \tab FabLab, West University of Timisoara. Timisoara, Romania.
% 	\item[2019] \tab 4D Cities, Multi-Actor Systems Department, TU Delft. Delft, Netherlands.
% 	\item[2019] \tab Mobile and Social Computing Lab, Fondazione Bruno Kessler. Trento, Italy.
% 	\item[2019] \tab ANET-Talks, ANET Lab, Hungarian Academy of Science. Budapest, Hungary.
% 	\item[2018] \tab Signa\_Lab, ITESO. Tlaquepaque, Mexico.
% 	\item[2015] \tab Encuentro de Urbanismo Alternativo, Centro Cultural de España en México. Mexico City, Mexico.
% 	\item[2015] \tab II Simposio de ciudades y territorios incluyentes \enquote{Derecho a la Ciudad}, Universidad Autónoma de Yucatán. Merida, Mexico.
% \end{tablist}

% \section*{Conference Presentations}
% Presenting author \textit{italicized}, if other.\bigskip
% \begin{tablist}
% 	\item[2019] \tab Natera Orozco, L. G., Deritei, D., Vancso, A., Vasarhelyi, O. \enquote{Quantifying life quality as walkability on urban networks} VIII Conference in Complex Networks and their Applications. Lisbon, Portugal. December 12-14.
% 	\item[2019] \tab Natera Orozco, L. G., Battiston, F., Iñiguez González, G., and Szell, M. \enquote{Multiplex urban fingerprints for bicycle infrastructure planning} Cycling Research Board Meeting. Delft, Netherlands. October 31-1 November.
% 	\item[2019] \tab Natera Orozco, L. G., Battiston, F., Iñiguez González, G., and Szell, M. \enquote{Multiplex urban fingerprints for bicycle infrastructure planning} 2019 NetSci. Burlington, Vermont. May 27-31.
% 	\item[2018] \tab Natera Orozco, L. G., Battiston, F., Szell, M. \enquote{Characterizing cities from their multiplex infrastructure patterns} SICC Workshop ComplexCity@PoliTo. Turin, Italy.
% 	\item[2013] \tab Natera Orozco, L. G. \enquote{Quiosco Libre, reading network in the public space} Future of Places. Stockholm, Sweden.
% \end{tablist}

% \subsection*{Posters}
% \begin{tablist}
% 	\item[2018] \tab Natera, L. \enquote{Budapest. Multilayer urban network} State of the Map. Milan, Italy.
% 	\item[2017] \tab Natera, L., Ábrego, V. \enquote{The evolution of twitter during the US elections} Data Stories. Budapest, Hungary.
% \end{tablist}

\section*{Grants and Fellowships}
\begin{tablist}
	\item[2020, 21] \tab Write-up grant. Central European University 
	\item[2019] \tab Registration grant. International Conference in Complex Networks and their Applications
	\item[2019] \tab Ph.D. conference travel grant. CEU Budapest Foundation
	\item[2019] \tab Registration grant. NetSci 
	\item[2018, 19] \tab Travel grant. Department of Network and Data Science, Central European University
	\item[2017--20] \tab Doctoral grant. Central European University. 
	\item[2015] \tab Academic Stay at MIT. Mexican National Council of Science and Technology
	\item[2013] \tab Master Studies Grant. Mexican National Council of Science and Technology
\end{tablist}

\section*{Detailed Teaching Experience}
\subsection*{GESIS – Leibniz Institute for the Social Sciences}
\begin{tablist}
	\item[2021] \tab  Introduction to Computation Social Sciences with Python. GESIS Fall Seminar in Computational Social Science. Co-taught with Orsyola Vásárhelyi
\end{tablist}

\subsection*{European Consortium for Political Research}
\begin{tablist}
	\item[2021] \tab Teaching Assistant, Python Programming for Social Scientists. Summer Virtual Methods School 2021
	\item[2021] \tab Teaching Assistant, Python Programming for Social Scientists. Winter Virtual Methods School 2021
	\item[2020] \tab Teaching Assistant, Python Programming for Social Scientists. Summer Virtual Methods School 2020
\end{tablist}

\subsection*{Central European University}
\begin{tablist}
	\item[2020] \tab Teaching Assistant, Scientific Python
	\item[2019] \tab Teaching Assistant, Statistical Methods in Network Science
\end{tablist}

\subsection*{ITESO}
\begin{tablist}
	\item[2019] \tab Network Science (Summer 2019) Invited lecturer, co-taught with Diego Arredondo (ITESO)
	\item[2017]	\tab Network Science (Summer 2017) Co-taught with Emma Towlson (Northeastern University), Sean P. Cornelius (Northeastern University), and Ricardo Zavala (ITESO)
	\item [2015--17]\tab Communication, Culture and Society (Spring 2016, 2017)
	\item [2015--16]\tab Social Systems Theory (Fall 2015, 2016)
\end{tablist} 

\end{document}