
\documentclass{academiccv}
\usepackage{color}

\begin{document}
\raggedright

% display name as the document title
\namefont{\myname}

% contact info
\vspace{1em}
\begin{minipage}[t]{0.495\textwidth}
  Department of Network and Data Science \\
  Central European University \\
  Nádor utca 11
  1051 Budapest, Hungary
\end{minipage}
\begin{minipage}[t]{0.495\textwidth}
  Office: N11, 608 \\
  Email: nateraluis@gmail.com \\
  https://luisnatera.com \\
  %Phone: +36-30-84
\end{minipage}
\vspace{0.5em}



\section*{Education}

\begin{tablist}

\item[Ph.D. ] \tab Network Science, Central European University, Budapest, 2020 (expected) \\
                  Dissertation: \textit{Multilayer Urban Networks} \\
                  Advisor: Federico Battiston \\
                  Co-Advisor: Michael Szell

\item[M.S.]  \tab Communication of Science and Culture, ITESO, Tlaquepaque. Mexico, 2015 \\
					Dissertation: \textit{La construcción de comunidades en red sobre conocimiento urbano en el marco del crecimiento urbano: Los blogs de espacio público}\\
					Advisor: Eduardo Quijano \\
					Committee: Rossana Reguillo, Francisco Morfín

\item[B.Arch.]  \tab Architecture,  ITESO, Tlaquepaque. Mexico, 2010

\end{tablist}



\section*{Academic Affiliations}

\begin{tablist}

\item[2016--17] \tab Executive Coordinator Signa\_Lab, Department of Sociocultural Studies, ITESO, Tlaquepaque. Mexico

\item[2015] \tab Visiting Student, Center for Civic Media,  Media Lab, Massachusetts Institute of Technology, Cambridge, MA. USA
\item[2008] \tab Visiting Student, Universidad de Valparaíso, Valparaíso, Chile.  

\end{tablist}



\section*{Research and Teaching Interests}

\begin{itemize}

\item Network science

\item Urban planning and mobility

\item Big data for social good

\item Data science and data visualization

\end{itemize}



\section*{Publications}

%\subsection*{Peer-Reviewed Journal Articles}

%\begin{tablist}

%\item[2018] \tab Boeing, G. \enquote{Pynamical: Model and Visualize Discrete Nonlinear Dynamical Systems, Chaos, and Fractals.} \textit{Journal of Open Source Education}, in press.


%\end{tablist}



%\subsection*{Journal Article Manuscripts Under Review}
\subsection*{Journal Article Preprints}
\begin{tablist}

\item[2019] \tab Natera Orozco, L. G., Battiston, F., I\~niguez, G., Szell, M. \enquote{Data-driven strategies for optimal bicycle network growth} \textit{ArXiv ID: 1907.07080}. 

\end{tablist}



\subsection*{Peer-Reviewed Book Chapters}

\begin{tablist}

\item[2019] \tab Natera Orozco, L. G. \enquote{Un cambio de la comunicación gubernamental y política. De los medios de comunicación a las redes sociales.} \textit{Informe Anual Q Medios 2018}, edited by Bernal, G. Jalisco, Mexico: ITESO.

\item[2018] \tab Natera Orozco, L. G., Reguillo, R. \enquote{Comunicación y cambio social: participación política e internet en Jalisco} \textit{Enciclopedia Jaliscience de la Comunicación.}, edited by Orozco, G., Reguillo, R. Jalisco, Mexico: Universidad de Guadalajara.

\end{tablist}

\subsection*{Reviews and Other Articles}

\begin{tablist}

\item[2016] \tab Natera Orozco, L. G., (as Signa\_Lab) \enquote{Battle of the hashtags: Mapping the online conversation surrounding Mexico's gas price} \textit{Global Voices.}

\end{tablist}


\subsection*{Proceedings, Reports, and Working Papers}

\begin{tablist}

\item[2019] \tab Natera Orozco, L. G., Deritei, D., Vancso, A., Vasarhelyi, O. \enquote{Quantifying life quality as walkability on urban networks} In: Cherifi H., Gaito S., Mendes J., Moro E., Rocha L. (eds) \textit{Complex Networks and Their Applications VIII. COMPLEX NETWORKS 2019. Studies in Computational Intelligence}, 2019, pp. 905–918.

\item[2014] \tab Natera Orozco, L. G. \enquote{Comunicación, ciudad e internet: flujos de información urbana en entornos digitales} VI Seminatio Internacional de Investigación en Urbanismo. Bogota, Colombia.

\end{tablist}



\subsection*{Manuscripts in Preparation and Development}

\begin{tablist}

\item[\the\year] Natera Orozco, L. G., Battiston, F., I\~niguez, G., Szell, M. \enquote{Cities classification by their multiplex infrastructure network} Target: \textit{Transport Findings}

\item[\the\year] Natera Orozco, L. G., Battiston, F., I\~niguez, G., Szell, M. \enquote{Dynamics of bicycle sharing systems, an analysis of 120M bike trips} Target: \textit{Environment and Planning B: Urban Analytics and City Science}

\end{tablist}


\section*{Invited Talks}

\begin{tablist}

\item[2019] \tab Data Science MeetUp. Timisoara, Romania.

\item[2019] \tab FabLab, West University of Timisoara. Timisoara, Romania.

\item[2019] \tab 4D Cities, Multi-Actor Systems Department, TU Delft. Delft, Netherlands.

\item[2019] \tab Mobile and Social Computing Lab, Fondazione Bruno Kessler. Trento, Italy.

\item[2019] \tab ANET-Talks, ANET Lab, Hungarian Academy of Science. Budapest, Hungary.

\item[2018] \tab Signa\_Lab, ITESO. Tlaquepaque, Mexico.

\item[2015] \tab Encuentro de Urbanismo Alternativo, Centro Cultural de España en México. Mexico City, Mexico.

\item[2015] \tab II Simposio de ciudades y territorios incluyentes \enquote{Derecho a la Ciudad}, Universidad Autónoma de Yucatán. Merida, Mexico.
\end{tablist}


\section*{Conference Activity}

%\subsection*{Conference Sessions Organized}

%\begin{tablist}

%\item[2017] \tab \enquote{Emerging Computational Methods in Urban Design.} American Collegiate Schools of Planning Annual Conference (ACSP). Denver, Colorado. Oct 12--15.

%\end{tablist}

%\subsection*{Conference Panels}

%\begin{tablist}

%\item[2017] \tab \enquote{Title} Panel member with "NAMES"; chaired by "NAME". CONFERENCE. WHERE. DAYS.

%\end{tablist}

\subsection*{Conference Presentations}

Presenting author \textit{italicized}, if other.\bigskip

\begin{tablist}
\item[2019] \tab Natera Orozco, L. G., Deritei, D., Vancso, A., Vasarhelyi, O. \enquote{Quantifying life quality as walkability on urban networks} VIII Conference in Complex Networks and their Applications. Lisbon, Portugal. December 12-14.

\item[2019] \tab Natera Orozco, L. G., Battiston, F., Iñiguez González, G., and Szell, M. \enquote{Multiplex urban fingerprints for bicycle infrastructure planning} Cycling Research Board Meeting. Delft, Netherlands. October 31-1 November.

\item[2019] \tab Natera Orozco, L. G., Battiston, F., Iñiguez González, G., and Szell, M. \enquote{Multiplex urban fingerprints for bicycle infrastructure planning} 2019 NetSci. Burlington, Vermont. May 27-31.

\item[2018] \tab Natera Orozco, L. G., Battiston, F., Szell, M. \enquote{Characterizing cities from their multiplex infrastructure patterns} SICC Workshop ComplexCity@PoliTo. Turin, Italy.

\item[2013] \tab Natera Orozco, L. G. \enquote{Quiosco Libre, reading network in the public space} Future of Places. Stockholm, Sweden.
\end{tablist}

\subsection*{Posters}

\begin{tablist}
	\item[2018] \tab Natera, L. \enquote{Budapest. Multilayer urban network} State of the Map. Milan, Italy.
	\item[2017] \tab Natera, L., Ábrego, V. \enquote{The evolution of twitter during the US elections} Data Stories. Budapest, Hungary.
\end{tablist}

\section*{Fellowships, Grants, and Awards}

\begin{tablist}
\item [2019] \tab Best lighting talk award. International Conference in Complex Networks and their Applications.

\item[2019] \tab Registration grant. International Conference in Complex Networks and their Applications

\item[2019] \tab Ph.D. conference travel grant. CEU Budapest Foundation
 
\item[2019] \tab Registration grant. NetSci 

\item[2018, 19] \tab Travel grant. Department of Network and Data Science, Central European University

\item[2015] \tab Academic Stay at MIT. Mexican National Council of Science and Technology

\item[2013] \tab Master Studies Grant. Mexican National Council of Science and Technology

\end{tablist}



\section*{Teaching Experience}

\subsection*{ITESO}

\begin{tablist}
	\item[2020] \tab Teaching Assistant, Scientific Python
	 
	\item[2019] \tab Teaching Assistant, Statistical Methods in Network Science
	 
	\item[2019] \tab Network Science (Summer 2019) Invited lecturer, co-taught with Diego Arredondo (ITESO)

	\item[2017]	\tab Network Science (Summer 2017) Co-taught with Emma Towlson (Northeastern University), Sean P. Cornelius (Northeastern University), and Ricardo Zavala (ITESO)

	\item [2015--17]\tab Communication, Culture and Society (Spring 2016, 2017)

	\item [2015--16]\tab Social Systems Theory (Fall 2015, 2016)


\end{tablist} 

\section*{Research Experience}

\begin{tablist}

\item[2015--17] 	\tab Researcher, Anillo Primavera. \\
								Principal Investigator: Sandra Valdes.

\item[2016] 	\tab Researcher, Online harassment of journalists and activists in Mexico, Jigsaw (formerly Google Ideas) and Global Voices. \\
							Principal Investigator: Ellery Biddle.

\item[2012] \tab Researcher, Public Transportation in Guadalajara. \\
						Principal Investigator: Mario Silva.

\end{tablist}


\section*{Academic Visits}

\begin{tablist}

	\item[2015] 	\tab Center for Civic Media, MIT Media Lab, Boston, USA, Jan - Jun

\end{tablist}


\section*{Service}
\subsection*{Journal Peer Review}
\begin{itemize}
  \item Scientific Data
\end{itemize}

\subsection*{Service to Department}
\begin{itemize}
  \item Ph.D. program representative, Central European University, DNDS, 2019-20
	\item Co-organizer Data Stories visualization exhibition, Central European University, DNDS, 2018-19
\end{itemize}


\section*{Professional Affiliations}
\begin{itemize}
	\item Network Science Society
	\item Python Software Foundation
	\item SICC Italian Society for Chaos and Complexity
\end{itemize}


\section*{Professional Experience}

\begin{tablist}

	\item[2020] \tab Latin American Capital, Senior Data Scientist Consultant. Guadalajara, Mexico.

	\item[2019] \tab Maven7US, City Data Scientist. Budapest, Hungary.

	\item[2015--17] \tab Mesura, Networks and Data Specialist. Guadalajara, Mexico.

	\item[2014] \tab Socialinks, Networks Consultant. Guadalajara, Mexico.

	\item[2014] \tab Institute for Mobility and Transportation of the State of Jalisco, Mobility Analyst. Zapopan, Mexico.

\end{tablist}



%\section*{Selected Recent Media Coverage}

%\begin{tablist}

%\item 2018 \tab \textit{Fast Company}. \enquote{How Crazy Is Your City's Plan?} Jul 16.

%\end{tablist}



\section*{Skills and Methods}

\subsection*{Statistical and Computational Methods}

\begin{itemize}

\item Network science methods
\item Programming, data wrangling and visualization: Python
\item Web: basic HTML/Javascript, Wordpress, Jekyll
\item Network visualization: Gephi, Cytoscape
\item Version control: Git +  GitHub
\item Other: \LaTeX, Adobe CS, CAD, QGIS, Blender

\end{itemize}


\subsection*{Languages}

\begin{itemize}

\item Spanish \tab Native
\item English \tab Professional proficiency

\end{itemize}



% display today's date as Month Year after a vertical space below the end of the text
\begin{center}
\vspace{6em}
%\vfill
Updated \monthyeardate\today
\end{center}



\end{document}
